Citeopotamus

### 2012-12-07 paper/paper.tex
Added a table

Given $n$ papers $(p_{1}, p_{2}, p_{3} ..., p_{n})$. We will let $RF(n_{i})$ be the number of references
for which we have full contextual information on and let $RT(n_{i})$ is the number of references
that were correctly placed in the paper.

Then we let our accuracy be:
$$Accuracy = \frac{\sum_{i = 1}^{m} RF(p_{i})}{\sum_{i = 1}^{m} RT(p_{i})}$$

@@

TODO(eriq): Table

>>>>

Given $n$ papers $(p_{1}, p_{2}, p_{3} ..., p_{n})$. We will let $RF(p_{i})$ be the number of references
for which we have full contextual information on and let $RT(p_{i})$ is the number of references
that were correctly placed in the paper $p_{i}$.

Then we let our accuracy be:
$$Accuracy = \frac{\sum_{i = 1}^{n} RF(p_{i})}{\sum_{i = 1}^{n} RT(p_{i})}$$

@@

\begin{table}[H]
\centering
\begin{tabular} { l | c | r }
\hline\hline
        {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
\hline
        ? & ? & ? \\[0.5ex]
\end{tabular}
\caption{Results}
\label{tab:results}
\end{table}
